Influence of Connectivity on Dung Beetle Communities

### 2025-03-03 corridor_docs/eric_ms_thesis/thesis_planning.Rmd

In the months of July and August 2024 dung beetles were sampled in 4 blocks spread across SRS, baited pitfall traps were placed in one of each patch type and in one matrix plot per block. Traps were placed in groups of 3 in the centers of each patch approximately 250 meters from the midpoint of the central patch 40 m from patch edge. Pitfalls were oriented in a triangular pattern with the bottom two traps positioned towards the center patch, each trap 20 m apart. Plots in the matrix were set up in a similar fashion with the center point 250 m from the center placed equidistant between adjacent patches.  For each sample period, traps were baited with pig dung between 8-9 pm and picked up 12 hours later, all beetles captured were stored in ethanol for further processing. In total 16 sampling rounds were carried out with 4 rounds per block, 196 samples were collected. All beetles of subfamily Scarabaeinae  were counted and identified to species using keys from @nemes_illustrated_2015 ### update bib. Overall 16 species were identified and approximately 5200 in total individual beetles were collected.

@@

>>>>

In the months of July and August 2024 dung beetles were sampled in 4 blocks spread across SRS, baited pitfall traps were placed in one of each patch type and in one matrix plot per block. Traps were placed in groups of 3 in the centers of each patch approximately 250 meters from the midpoint of the central patch 40 m from patch edge. Pitfalls were oriented in a triangular pattern with the bottom two traps positioned towards the center patch, each trap 20 m apart. Plots in the matrix were set up in a similar fashion with the center point 250 m from the center placed equidistant between adjacent patches.  For each sample period, traps were baited with pig dung between 8-9 pm and picked up 12 hours later, all beetles captured were stored in ethanol for further processing. In total 16 sampling rounds were carried out with 4 rounds per block, 196 samples were collected. All dung beetles were counted and identified to species with the exception of beetles of the genus Aphodius, overall 15 species were identified and approximately 5300 individual beetles were collected.

@@

1. total number of beetles _from_ total number of species 
1. were all species found in all habitats? Were any species found in only 1 habitat?
1. Were all species found in all blocks? Were any restricted to only 1-2 blocks?
1. Were all species found in the matrix? (expect that so, since it is the 'baseline' or 'source' habitat)
1. Number of species in each functional group
1. most common 3-4 species
1. any rare species?
